A comparative analysis of penalized linear mixed models in structured genetic data

### 2020-09-01 main.tex
2.3 edits

\pb{The flow of ideas here does not make sense to me; let's discuss} \anna{earlier or later paragraph} Whether or not such methods are effective at reducing confounding effects depends upon whether population structure can be accurately inferred. \anna{an important point to note, and one that we will return to later in 3.5, is that this only leads to confounding if pop structure is correlated with the environment...}
In the presence of environmental heterogeneity which affects the phenotype of interest, and which is not well-approximated by inferred population structure, SNP-phenotype associations will not be confounded. This is due to the absence of a causal pathway between population stratification and environment, as depicted in Figure \ref{fig:ps_env_block2}. In such a scenario, failing to account for unobserved environmental effects is likely to result in greater residual variability, however, SNP effect estimates will be unbiased \citep{greenland1999causal}. We will return to this idea and its mathematical justification in section \ref{sec:methods}.

@@

%------------------------------%
\subsection{Simulating environmental confounding}

>>>>

Whether or not such methods are effective at reducing confounding effects depends upon whether population structure can be accurately inferred. An important concept to note, and one that we will return to in section \ref{sec:sim_env_conf}, is that population structure only leads to confounding if it is correlated with the environment.
In the presence of environmental heterogeneity which affects the phenotype of interest, and which is not well-approximated by inferred population structure, SNP-phenotype associations will not be confounded. This is due to the absence of a causal pathway between population stratification and environment, as depicted in Figure \ref{fig:ps_env_block2}. In such a scenario, failing to account for unobserved environmental effects is likely to result in greater residual variability, however, SNP effect estimates will be unbiased \citep{greenland1999causal}. We will return to this idea and its mathematical justification in section \ref{sec:methods}.

@@

%------------------------------%
\subsection{Simulating environmental confounding}
\label{sec:sim_env_conf}
